### 2016-04-08 ms/ms_probaweb.tex
Compile in various formats

As a more explicit description of interactions among species, the
network approach offers a convenient representation of communities. Species
are represented as nodes and interactions by links. To date, studies of
network diversity have mostly been concerned with the distribution of
interactions within locations, and less so with the variation among locations
\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. There is however 
ample evidence that interaction networks vary in space and time
\citep{Laliberté2010, Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
theory provides explanation for the variation in the distribution of the
different nodes \citep{Gravel2011c, Pillai2011}, but there is no explanation
to the joint variation of node and link occurrences. We urgently need a
conceptual framework to formalize these observations.

@@

The methods used for rearing parasitoids from the galls have been
previously described by , Kopelke2003}. In brief, galls were
opened to score the presence of galler or parasitoid/inquiline larvae. Parasitoid
larvae were classified to preliminary morphospecies, and the identity of each
morphospecies was determined by connecting them to adults emerging after
hibernation. The galls were reared by storing single galls in small glass
tubes \citep{Kopelke1985a}. Hibernation of galls containing parasitoids took place
either within the glass tubes or between blotting paper in flowerpots filled
with clay granulate or a mixture of peat dust and sand. These pots were stored
over the winter in a roof garden and/or in a climatic chamber. In most cases,
the matching of larval morphospecies with adult individuals emerging from the
rearings allowed the identification of the parasitoids to the species
level. Nonetheless, in some cases, individuals could only be identified to one
of the (super)families Braconidae, Ichneumonidae, and Chalcidoidea. This was
particularly the case when only remains of faeces, vacant cocoons of
parasitoids, and/or dead host larvae were found, as was the case when
parasitoids had already emerged from the gall. As a result, the largest taxon
in the data set, ``Chalcidoidea indeterminate'', represents a superfamily of
very small parasitoids that are hard to distinguish.

@@

We restricted our framework to the effect of co-occurrence on ecological
interactions and neglected the inverse of the problem. We did not investigated
in depth the drivers of co-occurrence and simply took it for granted from the
data. Co-occurrence was indeed many times significantly different from the
expectation of independent species distribution. It thus raises the question
that, once accounting for the species-specific effect of the environment on
distribution, are there significant effects of interactions on co-occurrence?
We could rephrase this problem asking if the fundamental niche differs from
the realized niche, and how it applies to our framework. For example, we have
considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
which could be expanded as  $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. The
marginal occurrence probability, $P(X_{jy}|E_y )$, could be considered as a
species distribution model taking into account the interaction between these
species after some re-arrangement of Eq. 2. This derivation would however
critically depend on a strong a priori expectation of the conditional
probability of observing a species given the distribution of the other
species. This assumption seems reasonable for some situations, such as a
parasitoid species that requires a host to develop. On the other hand, we
found the strength of this association is often rather weak if not neutral
(with the example pair for instance analysed at Table 1). The lack of an
association could simply arises when the parasitoid is generalist enough so
that it is not constrained to track the distribution of its host
\citep{Cazelles2015}. At present, there is only indirect support to the
hypothesis that interacting species are conditionally distributed and it
should be the topic of more specific hypothesis testing. The impact of
ecological interactions on the distribution of co-occurrence has been the
topic of many publications since \citeal{Diamond1975} seminal study on
competition and the checkerboard distribution, but only recently pairwise
approaches received attention \citep{Veech2013}. It therefore remains unclear
if two interacting species are more closely associated in space because most
approaches based on null models consider community-level metrics (e.g.
\citealt{Gotelli2000}), such as the C-score, thereby making it hard to
evaluate if specific interactions do indeed affect co-occurrence. The
expansion of the framework we described to account for the difference between
the realized and the fundamental niche will therefore require further
investigation of the impact of interactions on co-occurrence.

>>>>

As a more explicit description of interactions among species, the
network approach offers a convenient representation of communities. Species
are represented as nodes and interactions by links. To date, studies of
network diversity have mostly been concerned with the distribution of
interactions within locations, and less so with the variation among locations
\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. There is however 
ample evidence that interaction networks vary in space and time
\citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
theory provides explanation for the variation in the distribution of the
different nodes \citep{Gravel2011c, Pillai2011}, but there is no explanation
to the joint variation of node and link occurrences. We urgently need a
conceptual framework to formalize these observations.

@@

The methods used for rearing parasitoids from the galls have been
previously described by \citealt{Kopelke2003}. In brief, galls were
opened to score the presence of galler or parasitoid/inquiline larvae. Parasitoid
larvae were classified to preliminary morphospecies, and the identity of each
morphospecies was determined by connecting them to adults emerging after
hibernation. The galls were reared by storing single galls in small glass
tubes \citep{Kopelke1985a}. Hibernation of galls containing parasitoids took place
either within the glass tubes or between blotting paper in flowerpots filled
with clay granulate or a mixture of peat dust and sand. These pots were stored
over the winter in a roof garden and/or in a climatic chamber. In most cases,
the matching of larval morphospecies with adult individuals emerging from the
rearings allowed the identification of the parasitoids to the species
level. Nonetheless, in some cases, individuals could only be identified to one
of the (super)families Braconidae, Ichneumonidae, and Chalcidoidea. This was
particularly the case when only remains of faeces, vacant cocoons of
parasitoids, and/or dead host larvae were found, as was the case when
parasitoids had already emerged from the gall. As a result, the largest taxon
in the data set, ``Chalcidoidea indeterminate'', represents a superfamily of
very small parasitoids that are hard to distinguish.

@@

We restricted our framework to the effect of co-occurrence on ecological
interactions and neglected the inverse of the problem. We did not investigated
in depth the drivers of co-occurrence and simply took it for granted from the
data. Co-occurrence was indeed many times significantly different from the
expectation of independent species distribution. It thus raises the question
that, once accounting for the species-specific effect of the environment on
distribution, are there significant effects of interactions on co-occurrence?
We could rephrase this problem asking if the fundamental niche differs from
the realized niche, and how it applies to our framework. For example, we have
considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
which could be expanded as  $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. The
marginal occurrence probability, $P(X_{jy}|E_y )$, could be considered as a
species distribution model taking into account the interaction between these
species after some re-arrangement of Eq. 2. This derivation would however
critically depend on a strong a priori expectation of the conditional
probability of observing a species given the distribution of the other
species. This assumption seems reasonable for some situations, such as a
parasitoid species that requires a host to develop. On the other hand, we
found the strength of this association is often rather weak if not neutral
(with the example pair for instance analysed at Table 1). The lack of an
association could simply arises when the parasitoid is generalist enough so
that it is not constrained to track the distribution of its host
\citep{Cazelles2015}. At present, there is only indirect support to the
hypothesis that interacting species are conditionally distributed and it
should be the topic of more specific hypothesis testing. The impact of
ecological interactions on the distribution of co-occurrence has been the
topic of many publications since \citealt{Diamond1975} seminal study on
competition and the checkerboard distribution, but only recently pairwise
approaches received attention \citep{Veech2013}. It therefore remains unclear
if two interacting species are more closely associated in space because most
approaches based on null models consider community-level metrics (e.g.
\citealt{Gotelli2000}), such as the C-score, thereby making it hard to
evaluate if specific interactions do indeed affect co-occurrence. The
expansion of the framework we described to account for the difference between
the realized and the fundamental niche will therefore require further
investigation of the impact of interactions on co-occurrence.
